IGRINS spectra of \name

### 2016-03-24 document/ms.tex
The manuscript sections now comport with the outline framework.

@@

@@

@@

\section{Methodology}\label{sec:methods} 
We extended an existing modular framework for spectral inference \citep[][hereafter \iancze]{2015ApJ...812..128C}.  We briefly summarize the model here for carity of notation, but see \iancze for more details.  We follow and expand the notation from \iancze, all summarized in Table \ref{table:params}.

@@

\subsection{Mixture model extension to \citet{2015ApJ...812..128C}}

@@

\subsection{Tuning the transition probability matrix for the highly degenerate mixture model}

@@

We combined our IGRINS spectroscopy with existing ESPaDOnS panchromatic optical echelle spectra to provide 88 spectral orders between 5100 and 25000 \AA \citep{2014MNRAS.444.3220D}.

\section{Analysis}
We compared the IGRINS spectrum of \name to the \PHOENIX grid of pre-computed synthetic model spectra \citep{2013A&A...553A...6H}.

@@

\section{Results}
We interpret the cooler temperatures derived at $K-$band as the presence of sunspots contributing more flux at longer wavelengths, as shown in the bottom panel of Figure \ref{fig:teffOrder}.  Here we show the absolute flux ratio, $f_{\lambda, B} / f_{\lambda, A}$ at two different temperatures: $T_\textrm{eff,A} = 4100$ and $T_\textrm{eff,B} = 3300$.  We present the ratio of two synthetic spectra from Phoenix (blue solid line), and the black body ratio (red dashed line).

@@

\subsection{Deriving $\teff$ in each IGRINS order}

@@

\section{Spectral properties}\label{sec:lines}

@@

\section{Technical details}

@@

\acknowledgements
The authors thank Gregory N. Mace for carrying out the IGRINS observations. This research has made use of NASA's Astrophysics Data System.

>>>>

\subsection{Pre Main Sequence HR diagram spread}

@@

\subsection{Previous studies of Starspots}

@@

\subsection{Previous studies of \name}

@@

\section{Methodology}\label{sec:methods}

\subsection{Full-spectrum fitting framework}
% Motivation for sampling- the questions we want to answer

We extended an existing modular framework for spectral inference \citep[][hereafter \iancze]{2015ApJ...812..128C}.  We briefly summarize the model here for carity of notation, but see \iancze for more details.  We follow and expand the notation from \iancze, all summarized in Table \ref{table:params}.

@@

\subsection{Approach 1: Deriving unique Teff in each order}

% Description of this approach

\subsection{Approach 2: Two component photosphere mixture model}

@@

\subsection{Challenges: Tuning the transition probability matrix}

@@

\subsection{ESPaDOnS Spectroscopy}
We combined our IGRINS spectroscopy with existing ESPaDOnS panchromatic optical echelle spectra to provide 88 spectral orders between 5100 and 25000 \AA \citep{2014MNRAS.444.3220D}.

\subsection{At what phase of variability were the spectra acquired?}

\section{Results}

\subsection{Result 1: Signal from deriving $\teff$ in each IGRINS order}

We compared the IGRINS spectrum of \name to the \PHOENIX grid of pre-computed synthetic model spectra \citep{2013A&A...553A...6H}.

@@

We interpret the cooler temperatures derived at $K-$band as the presence of sunspots contributing more flux at longer wavelengths, as shown in the bottom panel of Figure \ref{fig:teffOrder}.  Here we show the absolute flux ratio, $f_{\lambda, B} / f_{\lambda, A}$ at two different temperatures: $T_\textrm{eff,A} = 4100$ and $T_\textrm{eff,B} = 3300$.  We present the ratio of two synthetic spectra from Phoenix (blue solid line), and the black body ratio (red dashed line).

@@

@@

\subsection{Result 2: Effect size from fitting synthetic data order-by-order}

\subsection{Result 3: Direct measurement of spot properties with mixture model}

\section{Discussion}

\subsection{Interpretation of distribution of stellar properties from Results 1 + 2}

\subsection{Interpretation of star spot properties from Result 3}

\subsection{Longitudinal / latitudinal spot distributions and phase}

\subsection{Addressing limitations of assumptions in the methodology}

@@

\section{Testing and runing the mixture model}

@@

\acknowledgements
The authors thank Gregory N. Mace and Kyle Kaplan for carrying out the IGRINS observations. This research has made use of NASA's Astrophysics Data System.
